Abstract is the English version of the Intisari. It should be written in English with single line spacing and a maximum of 250 words. The abstract should contain what and why the research was conducted, how it was conducted, and what important results were obtained. It is recommended to write the abstract independently rather than using machine translation.

Example:

Real-time object detection is a crucial component in various computer vision applications such as autonomous vehicles and intelligent surveillance systems. The YOLOv8 architecture has demonstrated superior detection performance; however, its large model size poses a significant challenge for deployment on edge devices with limited computational resources. This research aims to develop an optimized YOLOv8 model through a combination of structured pruning and post-training quantization to enable efficient execution on the NVIDIA Jetson Nano platform. The methodology involves training a baseline model on the COCO 2017 dataset, applying structured pruning at ratios of 30\%, 50\%, and 70\% on the model's backbone and neck components, followed by fine-tuning and INT8 conversion using TensorRT. Experimental results demonstrate that the combination of 50\% pruning and INT8 quantization reduces the model size by 73\% and increases inference speed by 2.8$\times$ (from 12 FPS to 34 FPS on Jetson Nano) with only a 2.1\% decrease in mAP@0.5 compared to the baseline model. These findings indicate that the proposed optimization techniques are effective in producing a lightweight and fast object detection model without significantly compromising accuracy.

\vspace{2ex}
\noindent\textbf{Keywords: object detection, YOLOv8, pruning, quantization, edge device}
